List of publications

### 2025-03-13 report/CONJ_COMD.qmd
y in comparison plot

		data_comp <- do.call(ts.union, lapply(last_est_s, `[[`, "tc"))
		first_date <- time(last_est_s[[1]]$tc)[length(last_est_s[[1]]$tc)] - spec$plots$nyears
		range_y <- range(unlist(lapply(last_est_s, function(x) range(window(ts.union(x$tc), start = first_date)))))
		cat("\n\n::::: {.panel-tabset}\n")

>>>>

		data_comp <- do.call(ts.union, c(list("y" = last_est_s[[1]][["x"]]), lapply(last_est_s, `[[`, "tc")))
		first_date <- time(data_comp)[nrow(data_comp)] - spec$plots$nyears
		range_y <- range(window(data_comp, start = first_date))
		cat("\n\n::::: {.panel-tabset}\n")
